\thesistitle

### 2019-08-23 sections/discussion.tex
Working on discussion and results

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1). Often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\% more cloned nodes for T2). The main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types. T3R and T3 only a little bit higher than T2R and T2.

@@

>>>>

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. We see that the difference between T1R and T1 in terms of found clones is small (11\%). This implies that most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (35\%). Upon manual inspection we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.

@@

In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances. This graph is logaritmic: as the variability increases, the increase in nodes decreases. This implies that semantical equality increases the chances that tokens are equal.

In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes. The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear. This makes sense regarding the nature of the threshold. As we get into higher gap size percentages, fewer clones merge (thus the decrease in amount of clone classes merging). However, at these higher gap size percentages the gaps contains more nodes (thus the amount of cloned nodes being linear).

### 2019-08-23 sections/results.tex
Working on discussion and results

\subsection{Found nodes}
In this section, we display our results regarding the differences in found nodes between clone type % Sander:waar komt nodes ineens vandaan? ik ga uit van AST nodes maar is niet duidelijk denk ik
1-3~\cite{roy2007survey} and type 1R-3R. Figure~\ref{fig:typeres} shows the number of cloned nodes found over the entire corpus for the different clone types (the word ``Type'' is abbreviated as ``T''). For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between fragments to be considered clones. For type 3 and 3R clones, we allow a gap of 20\% the clones surrounding it.

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{img/TypeResults}
    \caption{Number of cloned nodes.}
\label{fig:typeres}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{img/DurationChart}
    \caption{Clone type performance.}
  \label{fig:performance}
  \end{minipage}
\end{figure}
% Sander: korte uitleg over wat we zien in de figures hier? (geld voor alle experimenten)

\subsection{Performance}
To map the viability of refactoring-oriented clone types for large scale clone detection, we measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. This figure shows the average duration of running CloneRefactor 10 times for a certain clone type. We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which do not have many background processes severely affecting the results. % Sander: zou zin na de komma (which..results) weglaten.
The durations are of course dependent on our implementation of the clone types.
% Sander: deze zin voegt ook niet zoveel toe

@@

@@

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrrrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
 & Same Method & 8,955 & 10.5\% & & \\ \midrule
\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
 & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
 & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
 & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
 & Ancestor & 199 & 0.2\% & & \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
 & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
 & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
 & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
 & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
\label{tab:location}
\end{table}

@@

\section{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments). The third column shows our measurements when restricting our search to method bodies. % Sander: waarom willen we dat weten?
The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
% Sander: die laatste zin snap ik niet
\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} & \textit{\textbf{Method Body}} & \textit{\textbf{\% (Method Body)}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\% & 26,109 & 50.4\% \\
Is Not A Partial Method & 21,625 & 25.3\% & 0 & 0.0\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% & 4,607 & 8.9\% \\
Spans Part of a Block & 12,964 & 15.2\% & 13,460 & 26.1\% \\
Multiple Return Values & 5,622 & 6.6\% & 6,131 & 11.9\% \\
Complex Control Flow & 1,106 & 1.3\% & 1,216 & 2.4\% \\
Overlap In Clone Class & 147 & 0.2\% & 147 & 0.3\% \\
Not In Class Or Interface & 70 & 0.1\% & 93 & 0.2\% \\
\bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}

>>>>

\subsection{Found nodes}
In this section, we display our results regarding the differences in the number of cloned nodes (see Section~\ref{sec:terminology} for our terminology) between clone type 1-3~\cite{roy2007survey} and type 1R-3R. Figure~\ref{fig:typeres} shows the number of cloned nodes found over the entire corpus for the different clone types (the word ``Type'' is abbreviated as ``T''). For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between fragments to be considered clones. For type 3 and 3R clones, we allow a gap size of 20\% the clones surrounding it (see Section~\ref{sec:t3rthreshold}).

\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{img/TypeResults}
    \caption{Number of cloned nodes.}
\label{fig:typeres}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{img/DurationChart}
    \caption{Clone type performance.}
  \label{fig:performance}
  \end{minipage}
\end{figure}

In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1). The difference between T2R and T2 is bigger (35\% more cloned nodes for T2). The number of cloned nodes of T3R and T3 are only a little bit higher than T2R and T2.

\subsection{Performance}
To map the viability of refactoring-oriented clone types for large scale clone detection, we measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. This figure shows the average duration of running CloneRefactor 10 times for a certain clone type. We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which allow for higher accuracy performance measurements as they do have limited background processes affecting the results. % Sander: zou zin na de komma (which..results) weglaten.
%The durations are of course dependent on our implementation of the clone types.

@@

In this graph, we see that the amount of clones increases as the amount of variability allowed increases. The graph is logaritmic: as the variability increases, the increase in nodes decreases.

@@

In this graph, we see a decrease in clone classes and an increase in cloned nodes when we increase the type 3R gap size threshold. We measure this threshold for a gap size of 0-200\%. In the graph, we see that both lines are rather linearly with minor jumps at certain thresholds. The jumps are at 33\%, 50\%, 100\%, 150\% and 200\%. The jump at 50\% is the largest. This makes sense regarding the nature of the threshold. At 50\%, all clone instances of 2 nodes with a gap of one node will merge into type 3R clones.

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrrrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
 & Same Method & 8,955 & 10.5\% & & \\ \midrule
\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
 & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
 & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
 & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
 & Ancestor & 199 & 0.2\% & & \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
 & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
 & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
 & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
 & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation.}
\label{tab:relation}
\end{table}

Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.

\subsection{Location}
Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a per location category.}
\label{tab:location}
\end{table}

We can see from these results that most clones are found at method level.

@@

From these results we see that 74\% of clones span part of a method body (77\% if we include constructors). 8\% of clones span several methods. 6\% of clones span only global variables. Only 4\% of clones span a full declaration (method, class, constructor, etc.).

\section{Extract Method}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments).
\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} \\ \midrule
Can Be Extracted & 24,157 & 28.2\%  \\
Is Not A Partial Method & 21,625 & 25.3\% \\
Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
Spans Part of a Block & 12,964 & 15.2\%  \\
Multiple Return Values & 5,622 & 6.6\%  \\
Complex Control Flow & 1,106 & 1.3\% \\
Overlap In Clone Class & 147 & 0.2\% \\
Not In Class Or Interface & 70 & 0.1\% \\
\bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}
